The Implications of Local Fluctuations in the Galactic Midplane for Dynamical Analysis in the \textit{Gaia} Era

### 2019-07-26 paper/ms.tex
Add changes from Robyn

\textbf{With the vast improvement in the quality of phase-space measurements
due to \textit{Gaia} the assumption of axisymmetry is increasingly inadequate
\citep[e.g.,][]{2018Natur.561..360A, 2019MNRAS.485.3134L}. The presence of the
phase-space spiral itself is evidence of disk oscillations
\citep{2018Natur.561..360A}, but the fact that its strength changes across the
disk is further evidence \citep{2019MNRAS.485.3134L, 2019MNRAS.486.1167B}. Even if the axisymmetric
assumption were close enough for many purposes, the parameters used in
axisymmetric models of the Galactic potential may be inadequately constrained
by current observations.}

@@

\textbf{We would like to emphasize that in reality one only ever measures the
position and velocity of a star at a single instance in time, and not over any
significant portion of its orbit. However, if more than one star on the same
orbit
     could be identified, then it would be possible
to constrain the disk potential in analogy to how stellar streams are
used to constrain the Galactic  potential
\citep[e.g.][]{1999ApJ...512L.109J, 2001ApJ...551..294I, 
2004ApJ...610L..97H, 2015ApJ...801...98S, 2015ApJ...803...80K,
2019MNRAS.483.1427L}. However, identifying the remnants of a disrupted open
cluster (the inner disk equivalent of a halo stellar stream) is a difficult
challenge. One
    possibility would be to use the stellar actions or other conserved quantities, but as we discuss in this
    work they are subject to substantial errors.  Another possibility would
    be to use
chemical tagging to identify a disrupted open cluster \citep{2002ARA&A..40..487F}, but
    this
may be difficult due to the large number of stars that are chemically
indistinguishable
    though
presumably born in different clusters
\citep{2018ApJ...853..198N}. An alternative technique that would deliver some
of the benefits of finding a disk stream may lie in measuring the
accelerations of stars \citep{2018arXiv181207581S}.}

>>>>

\textbf{With the vast improvement in the quality of phase-space measurements
due to \textit{Gaia} the assumption of axisymmetry is increasingly inadequate
\citep[e.g.,][]{2018Natur.561..360A, 2019MNRAS.485.3134L}. The presence of the
phase-space spiral itself is evidence of disk oscillations
\citep{2018Natur.561..360A}, but the fact that its strength changes across the
disk is further evidence \citep{2019MNRAS.485.3134L, 2019MNRAS.486.1167B}. Even if the axisymmetric
assumption were close enough for many purposes, the parameters used in
axisymmetric models of the Galactic potential may be biased by the non-axisymmetries in the disk.}

@@

\textbf{In reality one only ever measures the
position and velocity of a star at a single instance in time. However, there are at least two possibilities for going beyond a single temporal snapshot of the phase-space distribution. If more than one star on the same
or similar orbit
     could be identified (e.g., by identifying the remnants of a disrupted open cluster), then it would be possible
to constrain the disk potential in analogy to how stellar streams are
used to constrain the Galactic  potential
\citep[e.g.][]{1999ApJ...512L.109J, 2001ApJ...551..294I, 
2004ApJ...610L..97H, 2015ApJ...801...98S, 2015ApJ...803...80K,
2019MNRAS.483.1427L}. This would be challenging since, in principle, one would want to use the stellar actions or other conserved quantities, but as we discuss in this
    work they are subject to substantial errors.  Another possibility would
    be to use
chemical tagging to identify a disrupted open cluster \citep{2002ARA&A..40..487F}, but
    this
may be difficult due to the large number of stars that are chemically
indistinguishable
    though
presumably born in different clusters
\citep{2018ApJ...853..198N}. A second way to improve on a single temporal snapshot is to measure directly the
accelerations of stars \citep{2018arXiv181207581S}. While this would allow a direct measurement of the aliasing effect in Figure~\ref{fig:cartoon}, the observational challenges will likely limit this type of measurement to a small number of local stars for the near future.}
